\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-01-02 manuscript.Rnw
Use new plotting functions to create CEA plots

@@

\subsubsection{Representing decision uncertainty}
A number of common measures can be used to represent decision uncertainty from a CEA, including cost-effectiveness planes, cost-effectiveness acceptability curves (CEAC), cost-effectiveness acceptability frontiers (CEAF), and the expected value of perfect information (EVPI). Example plots of each from the code that follows are shown in Figure~\ref{fig:cea-plots}.

@@

<<ce_plane, fig.height = 3, fig.width = 4.5, fig.show="hide">>=
library("scales")
strategy_factor <- function (x) {
  factor(x, levels = 1:3, labels = c("SOC", "New 1", "New 2"))
}

xlim <- ceiling(max(cea_pw_ictstm$delta[, ie]) * 1.2)
ylim <- max(cea_pw_ictstm$delta[, ic]) * 1.2
ggplot(cea_pw_ictstm$delta,
       aes(x = ie, y = ic, col = strategy_factor(strategy_id))) +
  geom_jitter(size = .5)  +
  xlab("Incremental QALYs") +
  ylab("Incremental cost") +
  scale_y_continuous(limits = c(-ylim, ylim),
                     labels = scales::dollar) +
  scale_x_continuous(limits = c(-xlim, xlim), breaks = seq(-2, 2, .5)) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy") +
  geom_abline(slope = 100000, linetype = "dashed") +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0)
@

A useful summary measure for quantifying uncertainty is the CEAC, which can be generated based on simultaneous comparisons of all treatment strategies or by comparing each treatment strategy to a single comparator. The former is the probability that each strategy is the most cost-effective and is available from the \code{mce} element produced by \code{cea()}.

<<ceac_simultaneous, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
ggplot(cea_ictstm$mce,
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_colour_discrete(name = "Strategy") +
  theme(legend.position = "bottom")
@

The relevant information for the latter is available from the \code{ceac} element produced by \code{cea_pw()}, and is the probability that each treatment is more cost-effective than the comparator.

<<ceac_pw, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
ggplot(cea_pw_ictstm$ceac,
        aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

@@

<<ceaf, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
ggplot(cea_ictstm$mce[best == 1],
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

@@

<<evpi, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
ggplot(cea_ictstm$evpi, aes(x = k, y = evpi)) +
  geom_line()  +
  xlab("Willingness to pay") +
  ylab("Expected value of perfect information") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_y_continuous(label = scales::dollar) +
  theme(legend.position = "bottom")
@

>>>>

<<labels_indiv>>=
labs_indiv <- get_labels(hesim_dat, grp_label = NULL)
@

@@

\subsubsection{Representing decision uncertainty}
A number of common measures can be used to represent decision uncertainty from a CEA, including cost-effectiveness planes, cost-effectiveness acceptability curves (CEAC), cost-effectiveness acceptability frontiers (CEAF), and the expected value of perfect information (EVPI). Plots can be quickly generated with \code{plot_ceplane()}, \code{plot_ceac()}, \code{plot_ceaf()}, and \code{plot_evpi()} functions, respectively. Example plots from the code that follows are shown in Figure~\ref{fig:cea-plots}

@@

<<ce_plane, fig.height = 3, fig.width = 4.5, fig.show="hide">>=
plot_ceplane(cea_pw_ictstm, labels = labs_indiv)
@

The CEAC can be generated based on simultaneous comparisons of all treatment strategies or by comparing each treatment strategy to a single comparator. The former is the probability that each strategy is the most cost-effective and is available from the \code{mce} element produced by \code{cea()}. The relevant information for the latter is available from the \code{ceac} element produced by \code{cea_pw()}, and is the probability that each treatment is more cost-effective than the comparator.

<<ceac, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
plot_ceac(cea_ictstm, labels = labs_indiv)
plot_ceac(cea_pw_ictstm, labels = labs_indiv)
@

@@

<<ceaf, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
plot_ceaf(cea_ictstm, labels = labs_indiv)
@

@@

<<evpi, fig.height = 3, fig.width = 4.5, fig.show = "hide">>=
plot_evpi(cea_ictstm, labels = labs_indiv)
@
